msre design

### 2018-08-08 report/msredesign.tex
switched to figures insted of center (using [H] and float package) and added labels and refs. added figures from addendum cf-61-2-46

\documentclass{article}
\usepackage[active,tightpage]{preview}
\renewcommand{\PreviewBorder}{1in}

@@

\usepackage{graphicx}
\usepackage{caption}
\usepackage[autostyle]{csquotes}
\usepackage[style=authoryear,backend=biber]{biblatex}
\addbibresource{msredesign.bib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
}
\urlstyle{same}

@@

\usepackage{lipsum}
\begin{document}
\begin{preview}
\maketitle

@@

\section{core design}
the msre core design can be seen in figure 1 and figure 2, note that they differ slight, e.g. the vessel drain line and around the control rod.
\begin{center}
  \fbox{\includegraphics[page=5,width=0.8\textwidth,trim={2cm 6cm 3.5cm 4cm},clip]{./references/ORNL-TM-3229.pdf}}\\
  figure 1: MSRE reactor vessel \parencite[figure 1]{ornl-tm-3229}.
\end{center}
\begin{center}
  \fbox{\includegraphics[page=9,width=0.8\textwidth,trim={4cm 4cm 2.5cm 3cm},clip]{./references/ORNL-TM-0378.pdf}}\\
  figure 2: cutaway drawing of IGRE core and core vessel \parencite[figure 1]{ornl-tm-0378}.
\end{center}

\subsection{control rod and sample assembly}
the control rod and sample assembly is further detailed in figure 3.
\begin{center}
  \fbox{\includegraphics[page=10,width=0.8\textwidth,trim={3cm 9.5cm 3.5cm 8cm},clip]{./references/ORNL-TM-0378.pdf}}\\
  figure 3: msre control rod arrangements and typical fuel channels \parencite[figure 2]{ornl-tm-0378}.
\end{center}

\section{graphite rods}
the graphite moderator rod dimension, given in figure 4, are missing the angle of the spike, the dimensions of the pole, and disk at the bottom.
\begin{center}
  \centering
  \fbox{\includegraphics[page=6,width=0.8\textwidth,trim={3.5cm 6cm 2.5cm 5cm},clip]{./references/ORNL-TM-3229.pdf}}\\
  figure 4: typical graphite core block arrangement \parencite[figure 2]{ornl-tm-3229}.
\end{center}

the arangement of the graphite rods are detailed in figure 5
\begin{center}
  \centering
  \fbox{
  \includegraphics[page=10,width=0.42\textwidth,trim={1cm 3cm 0.25cm 4cm},clip]{./references/ORNL-TM-4174.pdf}
  \hspace{-0.2cm}
  \includegraphics[page=11,width=0.36\textwidth,trim={2cm 3.1cm 3cm 4cm},clip]{./references/ORNL-TM-4174.pdf}
  }\\
  figure 5: reactor core block assembly plan, drawing D-BB-B-40416 \parencite[page 10-11]{ornl-tm-4174}.
\end{center}

>>>>

\documentclass{article}
\usepackage[active,tightpage]{preview}
\renewcommand{\PreviewBorder}{1in}
\usepackage{float}

@@

\usepackage{graphicx}
\usepackage[figurename=figure]{caption}
\usepackage[autostyle]{csquotes}
\usepackage[style=authoryear,backend=biber]{biblatex}
\addbibresource{msredesign.bib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
}
\urlstyle{same}

@@

\begin{document}
\begin{preview}
\maketitle

@@

\section{core design}
the msre core design can be seen in figure \ref{3229-fig1} and figure \ref{0378-fig1}, note that they differ slight, e.g. the vessel drain line and around the control rod.
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=5,width=0.8\textwidth,trim={2cm 6cm 3.5cm 4cm},clip]{./references/ORNL-TM-3229.pdf}}
  \caption{msre reactor vessel \parencite[figure 1]{ornl-tm-3229}.}
  \label{3229-fig1}
\end{figure}
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=9,width=0.8\textwidth,trim={4cm 4cm 2.5cm 3cm},clip]{./references/ORNL-TM-0378.pdf}}
  \caption{cutaway drawing of IGRE core and core vessel \parencite[figure 1]{ornl-tm-0378}.}
  \label{0378-fig1}
\end{figure}

\subsection{control rod and sample assembly}
the control rod and sample assembly is further detailed in figure \ref{61246-fig14a}, \ref{61246-fig14b}, and \ref{61246-fig14c}.
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=23,width=0.8\textwidth,trim={4cm 2cm 4.8cm 2cm},clip]{./references/AD-CF-61-2-46.pdf}}
  \caption{msre control rod arrangement \parencite[figure 14a]{ad-cf-61-2-46}.}
  \label{61246-fig14a}
\end{figure}
% \begin{figure}[H]
%   \fbox{\includegraphics[page=10,width=0.8\textwidth,trim={3cm 9.5cm 3.5cm 8cm},clip]{./references/ORNL-TM-0378.pdf}}
%   \caption{msre control rod arrangements and typical fuel channels \parencite[figure 2]{ornl-tm-0378}.}
%   \label{0378-fig2}
% \end{figure}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=24,width=0.8\textwidth,trim={2.5cm 2cm 2.5cm 2.5cm},clip]{./references/AD-CF-61-2-46.pdf}}
  \caption{vertical section-poison control rod \parencite[figure 14b]{ad-cf-61-2-46}.}
  \label{61246-fig14b}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=25,width=0.8\textwidth,trim={2.5cm 2cm 2cm 1.5cm},clip]{./references/AD-CF-61-2-46.pdf}}
  \caption{msre control system \parencite[figure 14c]{ad-cf-61-2-46}.}
  \label{61246-fig14c}
\end{figure}

\subsection{graphite rods}
the graphite moderator rod dimension, given in figure \ref{3229-fig2}, are missing the angle of the spike, the dimensions of the pole, and disk at the bottom.
\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=6,width=0.8\textwidth,trim={3.5cm 6cm 2.5cm 5cm},clip]{./references/ORNL-TM-3229.pdf}}
  \caption{typical graphite core block arrangement \parencite[figure 2]{ornl-tm-3229}.}
  \label{3229-fig2}
\end{figure}

the arangement of the graphite rods are detailed in figure \ref{4174-p10-p11}
\begin{figure}[H]
  \centering
  \fbox{
  \includegraphics[page=10,width=0.42\textwidth,trim={1cm 3cm 0.25cm 4cm},clip]{./references/ORNL-TM-4174.pdf}
  \hspace{-0.2cm}
  \includegraphics[page=11,width=0.36\textwidth,trim={2cm 3.1cm 3cm 4cm},clip]{./references/ORNL-TM-4174.pdf}
  }
  \caption{reactor core block assembly plan, drawing D-BB-B-40416 \parencite[page 10-11]{ornl-tm-4174}.}
  \label{4174-p10-p11}
\end{figure}
